\documentclass[a4paper,landscape]{article}
\RequirePackage{tikz}
\RequirePackage[overlay]{textpos}
\setlength{\TPHorizModule}{1cm}
\setlength{\TPVertModule}{1cm}

%%%%%%%%%
% Fonts %
%%%%%%%%%
\RequirePackage[quiet]{fontspec}
\RequirePackage[math-style=TeX,vargreek-shape=unicode]{unicode-math}

\newfontfamily\bodyfont[]{HelveticaNeue LT 53 Ex}
\newfontfamily\thinfont[]{HelveticaNeue LT 23 UltLtEx}
\newfontfamily\headingfont[]{Elephant}
\newfontfamily\normalfont[]{Calibri}

\defaultfontfeatures{Mapping=tex-text}
\setmainfont[Mapping=tex-text, Color=textcolor]{HelveticaNeue LT 23 UltLtEx}


%%%%%%%%%%
% Colors %
%%%%%%%%%%

\RequirePackage{xcolor}

\definecolor{white}{RGB}{255,255,255}

\definecolor{darkgray}{HTML}{333333}
\definecolor{gray}{HTML}{4D4D4D}
\definecolor{lightgray}{HTML}{999999}

\definecolor{green}{HTML}{C2E15F}
\definecolor{orange}{HTML}{FDA333}
\definecolor{purple}{HTML}{D3A4F9}
\definecolor{red}{HTML}{FB4485}
\definecolor{blue}{HTML}{6CE0F1}

\colorlet{fillheader}{gray}
\colorlet{header}{white}
\colorlet{textcolor}{gray}
\colorlet{headercolor}{gray}


%%%%%%%%%%%%%
% Structure %
%%%%%%%%%%%%%
\RequirePackage{parskip}

\newcounter{colorCounter}
\def\@sectioncolor#1#2#3{%
  {%
    \color{%
      \ifcase\value{colorCounter}%
        blue\or%
        red\or%
        orange\or%
        green\or%
        purple\or%
        brown\else%
        headercolor\fi%
    } #1#2#3%
  }%
  \stepcounter{colorCounter}%
}

\renewcommand{\section}[1]{
  \par\vspace{\baselineskip}
  {%
    \LARGE\headingfont\color{headercolor}%
    \@sectioncolor #1%
  }
  \par\vspace{\baselineskip}
}

\renewcommand{\subsection}[2]{
  \par\vspace{.5\baselineskip}%
  \Large\headingfont\color{headercolor} #2%
  \par\vspace{.25\baselineskip}%
}

\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%
% List environment %
%%%%%%%%%%%%%%%%%%%%

\setlength{\tabcolsep}{0pt}
\newenvironment{entrylist}{%
  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}ll}
}{%
  \end{tabular*}
}
\renewcommand{\bfseries}{\headingfont\color{gray}}
\newcommand{\entry}[4]{%
  #1&\parbox[t]{16cm}{%
    \textbf{#2}%
    \hfill%
    {\footnotesize\addfontfeature{Color=lightgray} #3}\\%
    \normalfont#4\vspace{\parsep}%
  }\\}
  
\newcommand{\notitleentry}[2]{%
  #1&\parbox[t]{16cm}{%
    \normalfont#2%
    \hfill\\%
  }\\}


\usepackage[top=0in, bottom=0in, left=0in, right=1.5cm, nohead,nofoot]{geometry}

\begin{document}
\setlength{\fboxsep}{0pt}
 \colorbox{gray}{
  \begin{minipage}[t][\paperheight]{0.2\paperwidth}
    \begin{flushright}
        \fontsize{40pt}{72pt}\color{gray}{\_\_\_}% use this to keep the two minipage at the same top height
      \\
        \begin{textblock}{5.5}(0.2, 3)
        \begin{flushright}
            \fontsize{40pt}{72pt}\color{white}%
              {\bodyfont Soul}
             \vspace{0.3cm}\\
             \fontsize{14pt}{24pt}\color{white}%
              {\thinfont Zhao Xiang}
              \vspace{0.3cm}\\
             \fontsize{10pt}{12pt}\color{white}%
              {\thinfont Software Application Engineer}%
         \end{flushright}
        \end{textblock}

        \begin{textblock}{5.5}(0.2, 15)
        \begin{flushright}
            \let\oldsection\section
            \renewcommand{\section}[1]{
                    \par\vspace{\baselineskip}{\Large\headingfont\color{white} \hfill#1}
            }
            
            \section{Contact}
            \\
            {\fontsize{10pt}{12pt}\color{white}+86 151 0613 7119}
		        \\
            {\fontsize{10pt}{12pt}\color{white}soulzx2010@gmail.com}
            \\
            {\fontsize{10pt}{12pt}\color{white}github.com/soulzhao}
            \\            
            {\fontsize{10pt}{12pt}\color{white}Industry Park, Suzhou}
		  ~
            \let\section\oldsection
         \end{flushright}
        \end{textblock}
    \end{flushright}
\end{minipage}%
}
%
 \colorbox{white}{
\begin{minipage}[t][\paperheight]{0.7\paperwidth}
    \begin{flushleft}
%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{entrylist}
%------------------------------------------------
\entry
{2008 -- 2012}
{Bachelor of Computer Science}
{University of Science and Technology of Suzhou}
{Top 3 of the Computer Science and Technology department, and was selected as the best graduate representative for graduation ceremony.}
%------------------------------------------------
\end{entrylist}
%----------------------------------------------------------------------------------------
%   CAREER SECTION
%----------------------------------------------------------------------------------------
\section{Career}
\begin{entrylist}
%------------------------------------------------
\entry
{2012 -- Now}
{Oracle (China) Software System Co., Ltd}
{Suzhou, China}
{\emph{2 Years Fusion HCM Application Engineer} \\
Major in the development of Oralce’s Saas Product -- Fusion HCM system. I was in charge of the development and maintenance of the Costing module, and sometimes I would help on the BI Report module. Mainly use Java as the programming language. The youngest one that won the quarterly stars price(FY13, Q4) of Oracle CDC. \\}
%------------------------------------------------
\entry
{2011 -- 2012}
{Macronix (Suzhou) Co., Ltd   (Internship)}
{Suzhou, China}
{\emph{Associate Software Engineer} \\
Worked as an associate application engineer here for internship. Major in Android System optimization and linux driver development. I was in charge of the maintenance and development of the Sensor system on Android 2.3.\\}
%------------------------------------------------
\end{entrylist}
%----------------------------------------------------------------------------------------
%   PROJECT EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Projects}
\begin{entrylist}
%------------------------------------------------
\entry
{2014 -- Now}
{Electric Vehicle Information Gathering\&Analysis System}
{Institute Of Information Engineering, CAS}
{Cooperated with a post-doctoral in CAS, I, as a specialist for this National Project, am in charge of the information gathering and analysis. Using python, I wrote a spider to crawl hundreds of related websites to get specified information. I also impelemented a simple thread-pool to support multi-threads and use XML templates I defined the page structure to help customize the crawling. \\}
%------------------------------------------------
\entry
{2011 -- 2012}
{City Roads Maintenance\&Selection System For Emergency}
{Shanghai Jiao Tong University}
{Cooperated with a doctor in Shanghai Jiao Tong University, we worked together to finish this project. This is a C\# written program that contains many algorithms which could help not only simulate the real road conditions but also determine the right path for emergency. The algorithms I used are Dijistra Algorithm, MentoCarlo Algorithm, Genetic Algorithm and other frequently used algorithms for Graph data struture.\\}
%------------------------------------------------
\end{entrylist}
%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------
\section{Presentation}
\begin{entrylist}
\notitleentry
{Coding Skills:}
{I can use languages like Java, C\#, C/C++, Matlab, Python and so on (js, php, bash ...) to quickly complete the programming tasks. I'm familiar with Multi-threading, Design patterns and DB related knowledge. For algorithms, I take myself as a very quick learner and can pick up any algorithms in a short time.\\}
\notitleentry
{Communication Skills:}
{Good English commnunication skills, I can clearly express my ideas through writing and verbal communication.My communication skills leave a great impression on my current boss.\\}
\notitleentry
{Self-evaluation:}
{I consider myself as :A man who can quickly startup and being assigned to different tasks, A man who can learn things fast and is capable of resolving various issues, A man who is responsible and dedicated to his job.\\}
\end{entrylist}
    \end{flushleft}
\end{minipage}%
}
\end{document}